---
title: "help"
output: html_document
date: "2024-12-01"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
# This pulls the rows from dat_f14_index_procedure_for_vt from NOT the Homolce site (i.e., IKEM etc.) - to_insert

to_insert_og <- 
  cleaned_dat_list$dat_f14_index_procedure_for_vt |>
  filter(!str_starts(subjectId, "1-")) |>
  rename(dwell_time_min = ablationcathetertime) |>
  mutate(dwell_time = dwell_time_min * 60) |>
  select(subjectId, dwell_time_min, dwell_time)
```

```{r}
to_be_replaced_og <- cleaned_res |>
  filter(!str_starts(subjectId, "1-")) |>
  select(subjectId, dwell_time:etiology) 
```

We just realized that we're trying to match on different key classes

> class(to_insert_og$subjectId)
[1] "factor"
> class(to_be_replaced_og$subjectId)
[1] "character"

# Anonymize Data

```{r}
to_be_replaced <- structure(list(id = c("20", "21", "22", "23"
), df = c(NA_real_, NA_real_, NA_real_, NA_real_), factor = c("a", 
"a", "a", "a")), row.names = c(NA, -4L), class = c("tbl_df", 
"tbl", "data.frame"))
```

```{r}
to_insert <- structure(list(id = structure(20:23, levels = c("1", 
"2", "3", "4", "5", "6", "7", "8", 
"9", "10", "11", "12", "13", "14", "15", "16", "17", "18", "19", "20", "21", "22", "23", "24"), class = "factor"), df_min = c(1000, 1450, NA, NA
), df = c(60000, 90000, NA, NA)), row.names = c(NA, -4L), class = c("tbl_df", 
"tbl", "data.frame"))
```


# First Attempt - Use "replace"

```{r}
# This doesn't work
test_1.1 <- to_be_replaced |>
  mutate(df = replace(df, id == "20" | id == "21", to_insert[,"df"]))
```

```{r}
# This works but throws an error?
test_1.2 <- to_be_replaced |>
  mutate(df = replace(df, id == "20" | id == "21", to_insert$df))
```

# Second Attempt - Use "match"

In the future, we'll need to replace NAs from the Homolce dataset with values from the GLG source. This HAS to work

```{r}
#to_be_replaced = df
#df[match(to_insert$key, df$key), match(names(to_insert), names(df))] <- to_insert
#df
```

## Test to see if changing data types fixes all this - This did not

```{r}
#to_be_replaced <- to_be_replaced |> mutate(id = as.character(id))
#to_insert <- to_insert |> mutate(id = as.character(id))
```

```{r}
#to_be_replaced[match(to_insert$id, to_be_replaced$id), match(names(to_insert), names(to_be_replaced))] <- to_insert
```


```{r}
# This resets the order of subjectId
#tmp2 <- tmp[match(cleaned_res$subjectId, tmp$subjectId), ]
```

# For Loop

```{r}
# Make an empty vector to hold the results
tmp <- vector()
```

```{r}
# This works!
for(i in seq_along(1:length(res))) {
  tmp <- to_be_replaced_og[i,"subjectId"]
  to_be_replaced_og[to_be_replaced_og$subjectId == paste(tmp[[1]]),"dwell_time"] <- to_insert_og[to_insert_og$subjectId == paste(tmp[[1]]),"dwell_time"]
}
```

## Let's test with a different df

```{r}
for(i in seq_along(1:length(res))) {
  tmp <- to_be_replaced[i,"id"]
  to_be_replaced[to_be_replaced$id == paste(tmp[[1]]),"df"] <- to_insert[to_insert$id == paste(tmp[[1]]),"df"]
}
```

## Final Test

```{r}
id_to_replace <- cleaned_res |>
  filter(!str_starts(subjectId, "1-")) |> select(subjectId)

# These are the non-Homolce data for dwell time
dwell_to_insert <- 
  cleaned_dat_list$dat_f14_index_procedure_for_vt |>
  filter(subjectId %in% id_to_replace$subjectId) |>
  rename(dwell_time_min = ablationcathetertime) |>
  mutate(dwell_time = dwell_time_min * 60) |>
  select(subjectId, dwell_time_min, dwell_time)

for(i in seq_along(1:nrow(id_to_replace))) {
  tmp <- id_to_replace[i,"subjectId"]
  cleaned_res[cleaned_res$subjectId == paste(tmp[[1]]),"dwell_time"] <- dwell_to_insert[dwell_to_insert$subjectId == paste(tmp[[1]]),"dwell_time"]
}
```

