---
title: "Modify Raw Imported Data"
author: "Jonathan Salas"
date: "Last Updated `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(stringr)
knitr::opts_knit$set(root.dir = "~/R_Projects/VCAS1_prelim_efficiency")
```

# Start with a clean slate

```{r echo = F}
rm(list = ls(all.names = TRUE))
```

# Import the raw data - Point to the correct raw data directory

```{r}
raw_data_dir <- "data/processed/imported_efficiency_stats.RData"
```


## Import Subject Data
```{r}
load(raw_data_dir)
```

# Remove Empty Rows 

If the only thing populated is the ID, remove it

```{r}
#temp <- cleaned_res
#cleaned_res <- janitor::remove_empty(temp[, -1], which = "rows") |>
#  left_join(temp) |>
#  relocate(id)
```

# Exclude Patients

Exclude 1-011, procedure was aborted for safety reasons 

```{r}
cleaned_res <- cleaned_res |>
  filter(id != "1-011")
```

# Change Column Types

## Remove leading "1-" from each id name and convert to numeric scale
```{r}
cleaned_res <- cleaned_res |>
  mutate(id = as.numeric(str_remove(id, "^1-")))
```

## Calculate derived statistics

app_per_rove is how many applications we can get in within a minute of rove_time, bigger is better
proc_vs_rove is ratio of procedure time to rove time, bigger is better. 

```{r}
cleaned_res <- cleaned_res |>
  mutate(
    procedure_time_min = procedure_time/60,
    rove_time_min = rove_time/60,
    proc_vs_rove = procedure_time/rove_time,
    app_per_rove = num_applications/rove_time_min,
    across(where(is.numeric), \(x) round(x, 2))
  ) 
```

# Save cleaned data

```{r}
save(cleaned_res, 
     file = paste0("data/processed/working_efficiency_stats.RData"))
```

# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# Detach Packages before moving on

```{r}
invisible(lapply(paste0('package:', names(sessionInfo()$otherPkgs)), detach, character.only=TRUE, unload=TRUE)) # Detach Packages
```

# When were these files last rewritten?

```{r}
date()
```