---
title: "Import and Clean Data"
author: "Jonathan Salas"
date: "Last Updated `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
library(readxl)
library(janitor)
library(dplyr)
knitr::opts_knit$set(root.dir = "~/R_Projects/VCAS1_prelim_efficiency")
```

# Import the raw data - Point to the correct raw data directory

```{r}
raw_data_dir <-"data/raw/VCAS-I-rove_time.xlsx"
```

# Excel import

## Import Subject Data
```{r}
raw_res <- read_excel(path = raw_data_dir,
                      sheet = "results")
```

## Remove Empty Rows

```{r}
cleaned_res <- janitor::remove_empty(raw_res, which = "rows") |> select(-c(link_to_data, notes))
```

## Calculate derived statistics

proc_vs_rove is procedure time (seconds) as a function of rove_time (seconds)
rove_per_app is rove time (s) as a function of number of applications

```{r}
cleaned_res <- cleaned_res |>
  mutate(
    proc_vs_rove = round(procedure_time/rove_time,2),
    rove_per_app = round(rove_time/num_applications)
  ) 
```

# Save cleaned data

```{r}
save(cleaned_res, 
     file = paste0("data/processed/cleaned_efficiency_stats.RData"))
```

# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```
a
# When were these files last rewritten?
k
```{r}
date()
```