---
title: "Modify Raw Imported Data"
author: "Jonathan Salas"
date: "Last Updated `r format(Sys.time(), '%d %B, %Y')`"
output: html_document
---

```{r setup, include=FALSE}
library(dplyr)
library(stringr)
knitr::opts_knit$set(root.dir = "~/R_Projects/VCAS1_prelim_efficiency")
```

# Start with a clean slate

```{r echo = F}
rm(list = ls(all.names = TRUE))
```

# Import the raw data - Point to the correct raw data directory

```{r}
raw_data_dir <- "data/processed/imported_efficiency_stats.RData"
```

## Import the working data from the Procedural Summaries

```{r}
load("~/R_Projects/VCAS_Procedural_Summaries/data/processed/working_stats.RData")
```

## Import Subject Data
```{r}
load(raw_data_dir)
```

# Remove Empty Rows 

If the only thing populated is the ID, remove it

```{r}
#temp <- cleaned_res
#cleaned_res <- janitor::remove_empty(temp[, -1], which = "rows") |>
#  left_join(temp) |>
#  relocate(id)
```

# Exclude Patients

Exclude 1-011, procedure was aborted for safety reasons 
Drop 1-010 dwell time data because this is just catheter in/out and doesn't account for all the times we actually swap the catheter in and out

```{r}
cleaned_res <- cleaned_res |>
  filter(subjectId != "1-011") |> 
  mutate(dwell_time = replace(dwell_time, subjectId == "1-010", NA))
```

# REMOVE PROCEDURE TIME - We will use the GLG data for this, not your own

```{r}
cleaned_res <- cleaned_res |>
  select(-procedure_time)
```

# Change Column Types

## Convert to factor
```{r}
cleaned_res <- cleaned_res |>
  mutate(subjectId = factor(subjectId))
```

## Calculate derived statistics

### Use GLG timestamps for sites where we don't have footage to calculate dwell time

```{r}
# Identify all the non-Homolce VCAS data
id_to_replace <- cleaned_res |>
  filter(!str_starts(subjectId, "1-")) |> select(subjectId)

# These are the non-Homolce data for dwell time from GLG
dwell_to_insert <- 
  cleaned_dat_list$dat_f14_index_procedure_for_vt |>
  filter(subjectId %in% id_to_replace$subjectId) |>
  # We derive ablationcathetertime in the procedural summaries workflow
  rename(dwell_time_min = ablationcathetertime) |>
  mutate(dwell_time = dwell_time_min * 60) |>
  select(subjectId, dwell_time_min, dwell_time)

# Iteratively replace the cleaned_res dwell_time data with the one from GLG from the non-Homolce
for(i in seq_along(1:nrow(id_to_replace))) {
  tmp <- id_to_replace[i,"subjectId"]
  cleaned_res[cleaned_res$subjectId == paste(tmp[[1]]),"dwell_time"] <- dwell_to_insert[dwell_to_insert$subjectId == paste(tmp[[1]]),"dwell_time"]
}
```

### Do the math

app_per_rove is how many applications we can get in within a minute of rove_time, bigger is better
proc_vs_rove is ratio of procedure time to rove time, bigger is better. 

```{r}
cleaned_res <- cleaned_res |>
  mutate(
    dwell_time_min = dwell_time/60,
 #   procedure_time_min = procedure_time/60,
    rove_time_min = rove_time/60,
#    proc_vs_rove = procedure_time/rove_time,
    app_per_rove = numberapplications/rove_time_min,
    across(where(is.numeric), \(x) round(x, 2)),
    irrigation_delivered = (dwell_time/60)*6
  ) 
```

# Save cleaned data

```{r}
save(cleaned_res, 
     file = paste0("data/processed/working_efficiency_stats.RData"))
```

# Version and Package Details

```{r echo=F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# Detach Packages before moving on

```{r}
invisible(lapply(paste0('package:', names(sessionInfo()$otherPkgs)), detach, character.only=TRUE, unload=TRUE)) # Detach Packages
```

# When were these files last rewritten?

```{r}
date()
```