---
title: "Descriptive Statistics"
author: "Jonathan Salas"
date: "Last Updated `r format(Sys.time(), '%d %B, %Y')`"
output: 
  html_document: 
    df_print: kable
    fig_height: 6
    keep_md: true
---

```{r setup, include = FALSE}
#devtools::load_all("~/R_Projects/cv.tools")
library(ggplot2)
library(dplyr)
knitr::opts_chunk$set(echo = F)
knitr::opts_knit$set(root.dir = "~/R_Projects/VCAS1_prelim_efficiency")
```

# Start with a clean slate

```{r echo = F}
rm(list = ls(all.names = TRUE))
```

# Import - Point to the correct raw data directory

```{r}
raw_data_dir <- "data/processed/working_efficiency_stats.RData"
```

# Aesthetics

```{r}
blank.plot <- theme_bw() +
  theme(panel.border = element_blank(), 
        panel.grid.major = element_blank(), #this theme section generates a blank canvas
        panel.grid.minor = element_blank(), 
        axis.line = element_line(colour = "black"),
        legend.title = element_blank(),
        legend.justification = "top")
```

## load Subject Data
```{r}
load(raw_data_dir)
```

# Descriptive Statistics

Analysis Plan:
- histoplots of continuous variables - as of 7/30/24 this was useless to do, shows nothing at all due to small sample
- loess plots of continuous variables; x-axis is each procedure aligned in termporal order
- box plots
- we do procedure time vs rove time "proc_vs_rove" 

Hypotheses:

1) rove_per_app and rove_vs_proc with x axis as patient number to hopefully show a decreasing trend for both; i.e., you can 
  do lots of applications in a short period of time & ablation time is small relative to procedure time as the physician
  becomes more comfortable with our system
  
## The numbers

```{r}
cleaned_res |>
  summarise(
    mean_proc_min = mean(procedure_time_min, na.rm = T),
    sd_proc_min = sd(procedure_time_min, na.rm = T),
    mean_abl_min = mean(rove_time_min, na.rm = T),
    sd_abl_min = sd(rove_time_min, na.rm = T)
  )
```


### Make Mapping Data

Make temporary mapping data.

```{r}
# Make a procedure number column which is the patient id's numbered sequentially
temp_map_dat <- cleaned_res |>
  mutate(proc_num = seq_along(id))
```

## Procedure Time

#### Line Plot

```{r, warning = FALSE,message = FALSE,error = FALSE}
ggplot(data = temp_map_dat, aes(x = proc_num, y = procedure_time_min)) +
  geom_point(size = 5, aes(color = factor(proc_num))) +
  geom_smooth(span = 2, se = F) +
  scale_x_continuous(labels = temp_map_dat$proc_num, breaks = temp_map_dat$proc_num) +
  coord_cartesian(ylim = c(0,max(temp_map_dat$procedure_time_min) + 30)) + 
  xlab("Procedure Number") +
  ylab("Procedure Time (min)") +
  labs(caption = "Skin to skin time") +
  coord_cartesian(ylim = c(0,450)) +
  blank.plot +
  theme(axis.text = element_text(size = 40, face = "bold"),
        axis.title = element_text(size = 24,face ="bold")) 

ggsave("procedure_time_trend.png",
       path = "figures",
       scale = 1,
       width = 28,
       height = 21,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

#### Box Plots

```{r, warning=FALSE,message=FALSE,error=FALSE}
ggplot(data = temp_map_dat, aes(x = "", y = procedure_time_min)) +
  geom_boxplot() +
  geom_jitter(size = 5, aes(color = factor(proc_num))) + 
  xlab("") +
  ylab("Procedure Time (min)") +
  labs(caption = "Skin to skin time") +
  blank.plot +
  coord_cartesian(ylim = c(0,450)) +
  theme(axis.text = element_text(size = 40, face = "bold"),
        axis.title = element_text(size = 24,face ="bold")) +
  scale_y_continuous(position = "right")

ggsave("procedure_time_boxplot.png",
       path = "figures",
       scale = 1,
       width = 18,
       height = 21,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

## Ablation Time

#### Line Plot

```{r, warning = FALSE,message = FALSE,error = FALSE}
ggplot(data = temp_map_dat, aes(x = proc_num, y = rove_time_min)) +
  geom_point(size = 5, aes(color = factor(proc_num))) +
  geom_smooth(span = 2, se = F) +
  scale_x_continuous(labels = temp_map_dat$proc_num, breaks = temp_map_dat$proc_num) +
  coord_cartesian(ylim = c(0,max(temp_map_dat$rove_time_min) + 30)) + 
  xlab("Procedure Number") +
  ylab("Ablation Time (min)") +
  coord_cartesian(ylim=c(0,80)) +
  blank.plot +
  theme(axis.text = element_text(size=40, face = "bold"),
        axis.title = element_text(size=24,face = "bold")) 

ggsave("ablation_time_trend.png",
       path = "figures",
       scale = 1,
       width = 28,
       height = 21,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

#### Box Plots

```{r, warning = FALSE,message = FALSE,error = FALSE}
ggplot(data = temp_map_dat, aes(x = "", y = rove_time_min)) +
  geom_boxplot() +
  geom_jitter(size = 5, aes(color = factor(proc_num))) + 
  xlab("") +
  ylab("Ablation Time (min)") +
  labs(caption = "Represents sum procedure time spent performing ablation-related activities. ") +
  blank.plot +
  coord_cartesian(ylim = c(0,80)) +
  theme(axis.text=element_text(size=40, face = "bold"),
        axis.title=element_text(size=24,face = "bold")) +
  scale_y_continuous(position = "right")

ggsave("ablation_time_boxplot.png",
       path = "figures",
       scale = 1,
       width = 18,
       height = 21,
       units = "cm",
       dpi = "retina",
       limitsize = F)
```

# Save Results

# Version and Package Details

```{r echo = F}
paste(version$version.string, version$nickname)
paste0(
  "RStudio Version ",
  rstudioapi::versionInfo()$version,
  " ",
  rstudioapi::versionInfo()$release_name
) # RStudio Version
subset(data.frame(sessioninfo::package_info()),
       attached == TRUE,
       c(package, loadedversion)) # Loaded Packages
```

# When were these files last rewritten?

```{r}
date()
```